---
title: "Predicting Vision Visual Acuity based on Retinal Thickness"
author: "Dror Lichtenberg"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: TRUE
    toc: TRUE
mainfont: Century Gothic
fontsize: 12
urlcolor: blue
papersize: a4
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
---

```{r setup, include=FALSE}
# Load Libraries
# Todo: library("tidyverse")
# Todo: library("corrplot")

# Default Settings
knitr::opts_chunk$set(echo = TRUE)

# Load RDAs
# Todo: load("./rdas/data_summary.rda")

# Global parameters
# Todo: row_num <- dim(raw_data)[1]
# Todo: col_num <- dim(raw_data)[2]

```

\newpage
# Overview
## Executive Summary
<Todo: Add here after finishing the paper>

## Data-sources
<Todo: Add image for obtaining data and optional refernce to appendix "Adventures in obtaining data" (if exists ...), explain obfuscation >

## The Datasets
### Patients Data 
List of attributes in the dataset: <Todo: >

|# |Attribute            |Type                                   
|--|---------------------|-----------------------------------
|01|                     | 
|02|                     | 
|03|                     | 

### Clinical Summary Data
List of attributes in the dataset:  <Todo: >

|# |Attribute            |Type                                   
|--|---------------------|-----------------------------------
|01|                     | 
|02|                     | 
|03|                     | 


### OCT Examination Data 
List of attributes in the dataset:  <Todo: organize nice>


## Project Goal
**<Todo: Define with Ehud>**

<Todo: More details on goal/goals>

## Key Steps Performed 
### Data
1) Obtain Data: 
2) Consolidate and Tidy Cleaness: 
3) Beautify Attribute Names: Modified the column names to have title notations (capitalized and whith whitespaces instead of `.` delimiter).
4) Split Data Set:  Created the `train` and `test` data sets to be used for creating and evaluating the different algorithms.
5) Analyzed Data: Performed exploratory data analysis (EDA) and visualized the main attributes and relation between them.

### Methods 
1) Trained different models
2) Compared the results (accuracy and performance) of single models 
3) Evaluate ensemble approches

\newpage
# Data Analysis (Train Data Subset)
## Summary
Summary table below lists the attributes, grouped by the sickness classification

#```{r data_summary, echo=FALSE, message = FALSE}
#summary_table
#```

TODO: Note on which attribute seem to have greatest impact

## Key Attributes

## Relations Between Attributes

```{r correlation, echo=FALSE, message = FALSE}
#corrplot(cor(int_data[1:16]), type="lower", 
#                               method="color", 
#                               order="hclust", 
#                               tl.col="black", tl.srt=45)
```


\newpage
# Models and Results <ToDo: All >
## Naive Bayes Algorithm

## Logistic Regression Algorithm

## Random Forest Algorithm 

## Ensemble (???)

## Results comparison+

\newpage
# Conclusion  <ToDo: All >
## Summary

## Potential Impact,

## Limitations and Future Work
